imo

### 2025-04-08 inst/imo.Rmd
consistentification

```{r}
oecd <- read.csv("oecd.txt",header=FALSE)$V1
oecd
length(oecd)
oecd <- oecd[!(oecd %in% c("Chile", "Democratic People's Republic of Korea", "Turkiye"))]

@@

```{r}
for(i in seq_along(ranks)){
    jj <- ranks[[i]]
    ranks[[i]] <- jj[jj %in% oecd]
}
ranks
```

@@

```{r showlike}
alllike <- Reduce("*",like)
alllike 
alllike/max(alllike)
S <- log(alllike)
S <- S-max(S)
S <- pmax(S,-15)
round(S,2)
contour(S,levels = -(0:6)*2, lwd=c(1,4,1,1,1,1,1))
filled.contour(S)
```

>>>>

```{r}
oecd <- as.character(read.csv("oecd.txt",header=FALSE)$V1)
oecd

oecd <- oecd[!(oecd %in% c("Chile", "Democratic People's Republic of Korea", "Turkiye"))]

@@

```{r}
for(i in seq_along(ranks)){
    jj <- ranks[[i]]
    ranks[[i]] <- jj[jj %in% oecd]
}
```

@@

```{r showlike}
alllike <- Reduce("*",like)
S <- log(alllike)
S <- S-max(S)
S <- pmax(S, -9.999)
jj <- S
jj[jj < -9.99] <- NA
round(jj,2)
contour(a_try, x_try, S,
        xlab = "BT strength (scaled)", ylab = "x",
        levels = -(0:6)*2, lwd=c(1,4,1,1,1,1,1))
dim(S)
contour(a_try[1:8], x_try[6:17], S[1:8, 6:17], levels = -(0:6)*2, lwd=c(1,4,1,1,1,1,1))
filled.contour(S)
```

```{r}
like[[1]]
```
